---
title: "Exploratory Analysis of health procurements"
author: "preethi"
date: "8/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

From a given list of 9000 odd procurements from the state of Himachal Pradesh, we selected ~5000 health related procurements to analyse. 
We have include the details on how we went about selecting the procurment related data [here](https://docs.google.com/document/d/1Wb2PCqL0Fx2_Hz4Zuqpie0c5_z7ixHHGf5UwtBPtAls/edit)
First let us look at the data

```{r summary}
#rm(health_awards,patterns, health_contract)

#health_awards <- read.csv("health_award.csv", stringsAsFactors = FALSE)

#health_contract <- read.csv("merged_results_archive", stringsAsFactors = FALSE)
library(dplyr)
library(stringr)
library(xlsx)
library(tidyverse)

data_analysis <- read.csv("tenders_v_1 - tenders_v_1.csv", stringsAsFactors = FALSE)
#patterns <- read.xlsx("New Microsoft Excel Worksheet.xlsx", 1)

pattern1 <- c("medical", "hospital", "health")

data_text %>%
  filter_all(any_vars(str_detect(., 'text')))



```

patterns <- data.frame(word = c("Medical", "Hospital", "Health", "PHC", "CHC","ambulance","Medicine","diet","Food","Sanitation", "Sanitary","Sewerage","Sewage", "water","pump","pumping","rain","Pollution","Air quality","road","pulses","mustard","salt","microscope","biochemistry","WSS", "FIS", "tank", "GI","pipe", "radiograph","irrigation"), SDG = c("3.8","3.8","3.8", "3.8","3.8","3.8","3.8","2.1","2.1","3.3","3.3","3.3","3.3","6.1","3.3","3.3","6.1","3.9","3.9","3.6","2.1","2.1","2.1","3.c","3.c","6.4", "6.4", "3.3", "3.3", "3.3", "3.c", "6.4"))


for(i in seq_len(nrow(patterns))) {
  want <- grepl(patterns[i, "word"], data_analysis[, "tender.title"],ignore.case = T)
data_analysis[want, "SDG"] <- patterns[i, "SDG"]
}                                                                                                  
for(i in seq_len(nrow(patterns))) {
  want <- grepl(patterns[i, "word"], data_analysis[, "tender.description"],ignore.case = T)
 data_analysis[want, "SDG"] <- patterns[i, "SDG"]
} 

write.csv(data_analysis, "tenders_v2.csv")

#data_analysis %>% filter_all(any_vars(. %in% c('medicine', 'medical', 'hospital', 'health')))
  
```


patterns$Word <- as.character(patterns$Word)


 #for(i in seq_len(nrow(patterns))) {
  #  want <- grepl(patterns[i, "word"], health_awards[, "Title.and.Ref.No..Tender.Id"],ignore.case = T)
 #   health_awards[want, "pattern"] <- patterns[i, "pattern"]
#}


for(i in seq_len(nrow(patterns))) {
    want <- grepl(patterns[i, "Word"], data_analysis[,is.na("tender.title")],ignore.case =T)
    data_analysis[want, "SDG"]<- patterns[i,"SDG"]
}

#for(i in seq_len(nrow(patterns))) {
 #   want <- grepl(patterns[i, "keyword"], data_analysis[,is.na #("tender.description")],ignore.case = T)
 #   data_analysis [want, "SDG"] <- patterns[i, "SDG"]
#}

 
Coalese the different files 

library(dplyr)
data_analysis$pattern_work_desc <- coalesce(data_analysis$pattern_work_desc, data_analysis$pattern_tender_title)

data_analysis$pattern_work_desc <- coalesce(data_analysis$pattern_work_desc, data_analysis$pattern_title)

data_analysis$pattern_work_desc <- coalesce(data_analysis$pattern_work_desc, data_analysis$pattern_title_desc)

data_analysis$pattern_work_desc <- coalesce(data_analysis$pattern_work_desc, data_analysis$pattern_title)

data_analysis$pattern_work_desc <- coalesce(data_analysis$pattern_work_desc, data_analysis$pattern_title_1)

data_analysis$pattern_work_desc[is.na(data_analysis$pattern_work_desc)] <- "Other"


#health_awards$AOC.Date <- sub("(T).*$","",health_awards$AOC.Date)

#health_awards$AOC.Date <- as.Date(health_awards$AOC.Date, format = "%Y-%m-%d")

patterns$keyword <- as.character(patterns$keyword)

data_analysis$SDG_5 <- coalesce(data_analysis$SDG_5, data_analysis$SDG_4)

data_analysis$SDG_5<- coalesce(data_analysis$SDG_5, data_analysis$SDG_3)

data_analysis$SDG_5<- coalesce(data_analysis$SDG_5, data_analysis$SDG_2)

data_analysis$SDG_5<- coalesce(data_analysis$SDG_5, data_analysis$SDG_1)

#health_awards$AOC.Date <- sub("(T).*$","",health_awards$AOC.Date)

#health_awards$AOC.Date <- as.Date(health_awards$AOC.Date, format = "%Y-%m-%d")

## Plots

Adding plots 

library(ggplot2); library(dplyr); library(stringr); library(tidyr)

hist(health_awards$AOC.Date, "years",freq = TRUE)

 for(i in seq_len(nrow(patterns))) {
    want <- grepl(patterns[i, "word"], health_awards[, "Title.and.Ref.No..Tender.Id"],ignore.case = T)
    health_awards[want, "pattern"] <- patterns[i, "pattern"]
}


 for(i in seq_len(nrow(patterns))) {
    want <- grepl(patterns[i, "word"], health_awards[,"Tender.Description"], ignore.case = T)
    health_awards[want, "pattern"] <- patterns[i, "pattern"]
 }

health_awards$pattern <- as.character(health_awards$pattern)

health_awards$pattern[is.na(health_awards$pattern)] <- "Other"

health_awards$pattern_final <- paste(health_awards$Tender.Type, health_awards$pattern, sep ="-")

health_awards <- health_awards %>% separate(Organisation.Name, into = c("Org","Area","Sub_Area"), sep = "\\|\\|", extra = "merge")


awards_type <- health_awards %>% group_by(pattern_final) %>% summarise(total = sum(Contract.Value, na.rm = TRUE))

plot_award_type<- ggplot(data = awards_type, aes(x = pattern_final, y=total))
+geom_bar(stat = "identity")

plot_award_type
